Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-31 draft/paper1_jenny.tex
Edit color_ell 1

%% ------------------------------------------------------------------------------------ %% 
	The 1-D \mden{} profiles are extracted using single band image and the flux-weighted 
	shape of the isophote.  
	From the HSC images of these massive

	In addition to the shape of the light profile, we can also 
    study the $k$-corrected color profiles and ellipticity profiles 
    (computed via \texttt{Ellipse}) of these galaxies, and how 
    they depend on mass and environment.
    These quantities contain interesting information about the physical processes that 
    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
    our mass determinations because of systematic changes in color profile with stellar or 
    halo mass.

@@

    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
    (this is the range where we can safely ignore differences in sky subtraction and 
    seeing across different bands). 
    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color}. 
    We also compare our results with previous work based on stacking SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

>>>>

%% ------------------------------------------------------------------------------------ %% 
	Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	band image and the flux-weighted isophotal shape, while more useful information 
	can be gathered from the HSC images of these massive galaxies.
	The ellipticity and $k$-corrected optical color profiles are particularly 
	interesting.
	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
	isophote free. 
	And by applying the $i$-band isophotes to images of other bands in the 
	forced-photometry way, we can also measure the color profiles too. 
	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
	both the $g-r$ and $g-i$ color profiles.
	The PSF smearing effect will make the central isophotal shape rounder than the 
	real value, while the seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder when the seeing effect is not corrected.}. 
	At the same time, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
	becomes unstable and easily affected by any contamination; the color profile in
	the outskirt also becomes very sensitive to background level and noise level in 
	either band. 
	In this work, we will only

   These quantities contain interesting information about the physical processes that 
    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
    our mass determinations because of systematic changes in color profile with stellar or 
    halo mass.

@@

    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
    (this is the range where we can safely ignore differences in sky subtraction and 
    seeing across different bands).

    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color}. 
    We also compare our results with previous work based on stacking SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).
